TBD

### 2020-11-01 outputs/paper/paper.Rmd
Added some detail on the data

This research is about predicting who will win the US election. The election result has massive impact for the global population. The sitting president will set the tone for international and domestic policies.

@@

The survey data is provided by Nationscape (@citeNationscape).

@@

# Appendix {-}
Code and data are available at: https://github.com/karhian/2020-election

>>>>

This research is about predicting who will win the popular vote for the US election. The election result has massive impact for the global population. The sitting president will set the tone for international and domestic policies.

@@

The survey data is provided by Nationscape (@citeNationscape).Nationscapre conducts interview to 50,000 americans corvering the campaign and election. All responses take the survey online and must complete an attention check before taking the survey. Nationscape handles non-response by using a set of weights. The weights are devived from the the adult population of the 2017 American Community Survey of the U.S. Census Bureau.

@@

# Appendix {-}
